---
title: "Project WorkFlow"
author: "Néstor Narbona Chulvi"
date: "04/02/2022"
output: html_document
---

```{r}
library(tidyverse)
library(rtweet)
library(tidytext)
library(SnowballC)
library(entity)
library(ggridges) 
```

**0.Get tweets including 'Joe Biden' from the last week.**

```{r}
#tweets <- search_tweets("Biden", 
#                         n = 1000,
#                       since ="2021-12-18", #can only go 7 days back!
#                      until = "2021-12-25", 
#                        include_rts = FALSE, 
#                        retryonratelimit = TRUE)

tweets <- ds_tweets
```


**Retain only Tweets that include only the name 'Joe Biden' or only the name 'Biden'**
I want to do this so the sentiment valence of the tweet can be more validly interpreted as attitude towards Joe Biden. If there are more names in the tweet, it is unclear to which person the sentiment valence applies to. 

```{r}

names <- person_entity(tweets$text) #the function from entity that finds names

new_names <- matrix(NA,length(names),2)

#this forloop gives to each tweet one string containing all the names detected in the tweet
for(i in 1:length(names)){ 
  new_names[i,1] <- i
  new_names[i,2] <- ifelse(length(as.vector(unlist(names[i])))>0,paste(names[[i]], collapse = " "),NA)
}

tweets <- tweets%>%
  add_column(names = new_names[,2])

tweets_JB <- tweets%>% #containts tweets if and only if the mentioned Joe Biden or Biden
  filter(names %in% c('Joe Biden', 'Biden'))



```

**Taking users,links and code out of the tweets**
```{r}
tweets_JB$text <- gsub('http?\\S+','',tweets_JB$text) #delete links
tweets_JB$text<- gsub('<\\S+>','',tweets_JB$text) #delete weird code
tweets_JB$text <- gsub('@\\S+','',tweets_JB$text) #delete users


```

**Delete tweets containing interrogation marks**
This will make sentiment analysis more valid. 

```{r}
questions <- grep('[?]',tweets_JB$text)
tweets_JB <- tweets_JB[-(questions),]
```


**Retain only people who tweeted >n times**
At the moment, n>4
```{r}
active_users <- tweets_JB %>% 
  group_by(screen_name) %>% 
  mutate(activity = n())%>%
  filter(activity > 3)
```

**Looking for bots**
```{r}
active_users%>%
  count(user_id,sort = T)

active_users <- active_users%>%
  filter(screen_name != 'tankiebot69420')%>%
  filter(screen_name != 'PhilSmi50602350')%>%
  filter(screen_name != 'DuRoRoDu')%>%
  filter(screen_name != 'VippusaO')%>%
  filter(screen_name != 'TomthunkitsMind')%>%
  filter(screen_name != 'yhwh2be')%>%
  filter(screen_name != 'shatermhmd')%>%
  filter(screen_name != 'MAGA20222')

```


**Measure involvement**
I obtain political words from Oxford Learner's Dictionaries on the category Politics (including Election, Government, International relations, Parilamente, Political views and systems, Politicians). This method will have some problems regarding capturing popular political vocabulary. Some specificity problems are expected as the corpus includes some general terms such as 'marginal' (this could be solved by looking at what words of the lexico are more frequent in tweets obtained from non-political hash tags). 

Source: https://www.oxfordlearnersdictionaries.com/topic/politics?sublist=politicians_t

```{r}
text <- 'absentee ballotnounC2    
abstainverbC2    
abstentionnounC2    
alternative votenounC2    
apathynounC2    
attack adnounC2    
ballotnounC1    
ballot boxnounC2    
bundlernounC2    
by-electionnounC2    
campaignnounB1    
candidacynounC2    
candidaturenounC2    
canvassnounC2    
canvassverbC2    
canvassernounC2    
congressional districtnounC2    
constituencynounC1    
constituentnounC2    
contestnounB2    
contestverbB2    
depositnounC2    
deselectverbC2    
dirty tricknounC2    
disenfranchiseverbC2    
electverbB2    
electableadjectiveC1    
electionnounB1    
electioneeringnounC2    
electiveadjectiveC2    
electornounC2    
electoraladjectiveC1    
electoral collegenounC2    
electoratenounC1    
enfranchiseverbC2    
enfranchisementnounC2    
exit pollnounC2    
first-past-the-postadjectiveC2    
floating voternounC2    
franchisenounC2    
general electionnounC1    
hustingsnounC2    
incomingadjectiveC2    
landslidenounC2    
majoritynounB2    
mandatenounC1    
manifestonounC1    
marginaladjectiveC2    
marginalnounC2    
national conventionnounC2    
nominateverbC1    
nominationnounC1    
off yearnounC2    
outgoingadjectiveC2    
overall majoritynounC2    
pollnounC1    
pollingnounC1    
polling boothnounC2    
polling daynounC2    
polling stationnounC2    
popular votenounC2    
postal votenounC2    
primarynounC2    
protest votenounB2    
psephologistnounC2    
psephologynounC2    
push pollnounC2    
push pollingnounC2    
referendumnounC1    
resultnounA1    
runverbB2    
running matenounC2    
safe seatnounC2    
soft moneynounC2    
standverbB2    
straw pollnounC2    
swing statenounC2    
swing votenounC2    
swing voternounC2    
ticketnounC2    
turnoutnounC1    
unelectedadjectiveC1    
votenounB1    
voteverbB1    
voternounB1    
votingnounB2    
voting boothnounC2    
voting machinenounC2
agencynounB2    
autonomousadjectiveC2    
budgetnounB2    
bureaunounC1    
bureaucracynounC1    
bureaucratnounC2    
cabinetnounC1    
the civil servicenounC2    
civil servantnounC1    
coalitionnounC1    
commissionernounC2    
communiquénounC2    
constitutionnounC1    
constitutionaladjectiveC1    
constitutionallyadverbC1    
corporationnounC2    
councilnounB2    
crownnounC1    
departmentnounA2    
destabilizeverbC2    
domesticadjectiveB2    
the executive branchnounC2    
executive ordernounC2    
executive privilegenounC2    
governverbB2    
governmentnounA2    
the Home OfficenounC2    
the judicial branchnounC2    
kleptocracynounC2    
kleptocraticadjectiveC2    
lawnounA2    
lawfuladjectiveC2    
leadernounA2    
the legislative branchnounC2    
line-item vetonounC2    
massnounB2    
ministerialadjectiveC2    
ministrynounC1    
municipalitynounC2    
officenounA2    
policymakernounC1    
policymakingnounC1    
power grabnounC2    
rainbow coalitionnounC2    
red tapenounC2    
regime changenounC1    
rulenounB2    
ruleverbB1    
rulernounB1    
rulingnounC1    
secretarynounB2    
statenounA2    
stateadjectiveB1    
the State of the Union AddressnounC2    
town hallnounB1    
alliancenounC1    
alliedadjectiveC1    
allynounC1    
ambassadornounC1    
arenanounC1    
arms controlnounC2    
axisnounC2    
balance of powernounC2    
bilateraladjectiveC2    
blocnounC2    
bordernounB1    
bridge-buildingnounC2    
brokerverbC2    
colonialismnounC2    
colonialistadjectiveC2    
colonialistnounC2    
commercenounC1    
common marketnounC1    
compactnounC2    
confederationnounC2    
conflictnounB2    
conventionnounC1    
cross-borderadjectiveC2    
customs unionnounC2    
detentenounC2    
dialoguenounB2    
diplomacynounC1    
diplomatnounC1    
diplomaticadjectiveC1    
the Diplomatic ServicenounC2    
diplomaticallyadverbC1    
diplomatic bagnounC2    
diplomatic corpsnounC2    
diplomatic immunitynounC2    
diplomatistnounC2    
economynounB1    
embassynounC1    
ententenounC2    
EUabbreviationB1    
the European UnionnounB1    
foreignadjectiveA2    
the Foreign SecretarynounC2    
the Foreign, Commonwealth and Development OfficenounC2    
Foreign ServicenounC2    
free tradenounC1    
frontiernounC1    
geopoliticaladjectiveC2    
geopoliticsnounC2    
globalizationnounB2    
good-neighbourlinessnounC2    
hard powernounC2    
human rightnounB2    
imperialistadjectiveC2    
independencenounB2    
independentadjectiveA2    
intergovernmentaladjectiveC2    
internationaladjectiveA2    
internationalismnounC2    
internationalistnounC2    
internationalistadjectiveC2    
internationallyadverbB1    
isolationismnounC2    
isolationistnounC2    
isolationistadjectiveC2    
multilateraladjectiveC2    
multilateralismnounC2    
NATOabbreviationC1    
negotiateverbB2    
negotiationnounB2    
neocolonialismnounC2    
non-aggressionnounC2    
non-interventionnounC2    
non-interventionismnounC2    
non-interventionistadjectiveC2    
partitionnounC2    
political geographynounC2    
power politicsnounC2    
rapprochementnounC2    
relationnounB1    
relationshipnounA2    
resolutionnounC1    
the Schengen agreementnounC2    
soft powernounC2    
summitnounC1    
thawverbC2    
thawnounC2    
tradenounB1    
transatlanticadjectiveC1    
transnationaladjectiveC2    
treatynounC1    
the United NationsnounB1  
actnounB1    
assemblynounC1    
back benchnounC2    
benchnounC2    
billnounB2    
capitolnounC2    
chambernounC1    
the CommonsnounC2    
conference committeenounC2    
congressnounB2    
congressionaladjectiveC1    
debatenounB2    
debateverbB2    
executivenounC1    
the House of CommonsnounC2    
the House of LordsnounC2    
the House of RepresentativesnounC2    
the Houses of ParliamentnounC1    
inauguraladjectiveC2    
inauguralnounC2    
inaugurateverbC2    
inaugurationnounC2    
Inauguration DaynounC2    
the Leader of the HousenounC2    
the Leader of the OppositionnounC2    
legislateverbC1    
legislationnounC1    
legislativeadjectiveC1    
legislaturenounC1    
lobbynounC2    
lobbyverbC1    
minority governmentnounC2    
oppositionnounB2    
pairingnounC2    
parliamentnounB2    
parliamentaryadjectiveC1    
parliamentary privilegenounC2    
passverbB2    
passagenounC2    
passingnounC1    
pentagonnounC2    
press gallerynounC2    
propositionnounC1    
prorogueverbC2    
recessnounC2    
repealnounC2    
repealverbC2    
seatnounB2    
second chambernounC2    
senatenounC1    
sessionnounB2    
sitverbC2    
state housenounC2    
statutenounC2    
statute lawnounC2    
upper chambernounC2    
upper housenounC2    
WestminsternounC2
absolutismnounC2    
activismnounC1    
activistnounC1    
affairnounB2    
agitpropnounC2    
alt-rightnounC2    
anarchismnounC2    
anarchistnounC2    
anarchynounC2    
AntifanounC2    
apoliticaladjectiveC2    
autonomynounC1    
BrexitnounC2    
BrexiteernounC2    
brinkmanshipnounC2    
capitalismnounC1    
centernounB2    
centralismnounC2    
centralistadjectiveC2    
centrenounB2    
centristnounC2    
centristadjectiveC2    
collectivismnounC2    
collectivistadjectiveC2    
communismnounC1    
communistnounC1    
the Communist PartynounC1    
comradenounC2    
Con.abbreviationC2
conservatismnounC2    
conservativeadjectiveB2    
conservativenounB2    
the Conservative PartynounB2    
constitutionalismnounC2    
constitutionalitynounC2    
constitutional monarchynounC2    
coupnounC1    
current affairsnounC1    
Dem.abbreviationC2
democracynounB2    
democratnounB2    
democraticadjectiveB2    
the Democratic PartynounB2    
despotnounC2    
devolutionnounC2    
devolvedadjectiveC2    
devolve onphrasal verbC2
devolve tophrasal verbC2
devolve uponphrasal verbC2
dictatornounC1    
dictatorshipnounC1    
dissidencenounC2    
dissidentnounC2    
dissidentadjectiveC2    
divine rightnounC2    
dog whistlenounC2    
egalitariannounC2    
egalitarianadjectiveC2    
egalitarianismnounC2    
exilenounC1    
expansionismnounC2    
expansionistnounC2    
expansionistadjectiveC2    
extremismnounC1    
extremistnounC1    
extremistadjectiveC1    
fanaticnounC2    
fanaticaladjectiveC2    
fanaticallyadverbC2    
fanaticismnounC2    
fascismnounC2    
fascistadjectiveC2    
fascistnounC2    
federaladjectiveB2    
federal governmentB2    
federalismnounC1    
federalistadjectiveC1    
federalistnounC1    
federallyadverbB2    
federationnounC1    
fellow travellernounC2    
feudaladjectiveC2    
feudalismnounC2    
globalismnounC1    
globalistnounC1    
globalistadjectiveC1    
greenadjectiveB1    
greennounB2    
hard leftnounC2    
hard rightnounC2    
idealnounB2    
idealismnounC2    
identity politicsnounC2    
ideologicaladjectiveC1    
ideologicallyadverbC1    
ideologuenounC2    
ideologynounC1    
imperialismnounC2    
imperialistnounC2    
interest groupnounC2    
interventionismnounC2    
interventionistnounC2    
interventionistadjectiveC2    
kingnounA2    
Lab.abbreviationC2
labournounB2    
the Labour PartynounB2    
leaguenounB2    
leavernounC2    
leftnounB1    
leftismnounC2    
leftistadjectiveC2    
leftistnounC2    
left wingnounC1    
left-wingadjectiveC1    
left-wingernounC1    
LeninismnounC2    
LeninistadjectiveC2    
LeninistnounC2    
Lib DemabbreviationC2    
liberaladjectiveC1    
the Liberal DemocratsnounC2    
liberalismnounC1    
libertariannounC2    
mainstreamnounC1    
MarxismnounC2    
MarxistnounC2    
MarxistadjectiveC2    
militarismnounC2    
militaristnounC2    
militaristicadjectiveC2    
moderateadjectiveC1    
moderatenounC1    
monarchnounB2    
monarchynounB2    
movementnounB1    
nationalismnounC2    
nationalistadjectiveC2    
nationalistnounC2    
nationalisticadjectiveC2    
neoconservativeadjectiveC2    
neoconservativenounC2    
neoliberaladjectiveC2    
neoliberalismnounC2    
non-partisanadjectiveC2    
non-violencenounC2    
non-violentadjectiveC2    
oligarchynounC2    
PACabbreviationC2    
pacifismnounC2    
pacifistadjectiveC2    
pacifistnounC2    
partynounB1    
party linenounC2    
party politicaladjectiveC2    
party political broadcastnounC2    
party politicsnounC2    
people powernounC2    
platformnounC2    
police statenounC1    
policynounB1    
politicaladjectiveB1    
political action committeenounC2    
political capitalnounC2    
politicallyadverbB1    
political sciencenounC1    
political scientistnounC1    
politicsnounB1    
populismnounC2    
populistadjectiveC2    
populistnounC2    
powernounA2    
pressure groupnounC2    
pro-prefixC1    
propagandanounC1    
proportional representationnounC2    
queennounA2    
radicaladjectiveC1    
radicalnounC1    
radicalismnounC2    
rallynounC1    
reactionaryadjectiveC2    
reactionarynounC2    
redadjectiveC1    
rednounC1    
reformnounC1    
reformverbC1    
reformernounC1    
reformistadjectiveC2    
regimenounC1    
RemainernounC2    
RemoanernounC2    
Rep.abbreviationC2
representativeadjectiveC1    
republicnounC1    
republicannounC2    
republicanadjectiveC2    
the Republican PartynounC1    
republicanismnounC2    
revisionistadjectiveC2    
revisionistnounC2    
revoltnounC2    
revoltverbC2    
revolutionnounB2    
revolutionaryadjectiveC1    
revolutionarynounC1    
the right wingnounC1    
rightistnounC2    
rightistadjectiveC2    
right-wingadjectiveC1    
right-wingernounC1    
the Scottish National PartynounB2    
secularismnounC2    
secularistadjectiveC2    
slogannounB2    
smearverbC2    
smearnounC2    
socialismnounC1    
socialistadjectiveC1    
special interest groupnounC2    
speechnounA2    
spinnounC2    
statismnounC2    
statistadjectiveC2    
statistnounC2    
supportverbA2    
supporternounB1    
TorynounC2    
ToryadjectiveC2    
ToryismnounC2    
tyrantnounC2    
unilateralismnounC2    
unilateralistnounC2    
unilateralistadjectiveC2    
unrestnounC2    
uprisingnounC2    
utilitarianadjectiveC2    
utilitarianismnounC2    
utopianadjectiveC2    
utopianismnounC2    
wingnounC1    
witch-huntnounC2  
backbenchernounC2    
chancellornounC2    
Chief WhipnounC2    
congresswomannounB2    
councillornounC1    
demagoguenounC2    
deputynounC1    
FLOTUSabbreviationC2    
the front benchnounC2    
governornounB2    
Home SecretarynounC2    
independentnounC1    
leadershipnounB2    
legislatornounC1    
majority whipnounC2    
mayornounB2    
Member of CongressnounB2    
Member of ParliamentnounB1    
ministernounB2    
MPnounB1    
oligarchnounC2    
parliamentariannounC2    
PMnounB2    
politiciannounB1    
POTUSabbreviationC2    
premiernounC2    
presidentnounA2    
prime ministernounB1    
representativenounB2    
Secretary of StatenounC2    
senatornounC1    
shadowadjectiveC2    
speakernounC2    
spin doctornounC2    
spokesmannounB2    
spokespersonnounB2    
spokeswomannounB2    
statesmannounC1    
whipnounC2'

A <- gsub('C\\d|B\\d|A\\d',",",text) #delete english level
A <- gsub('\n','',A)
A <- gsub('noun|verb|adjective|pronoun','',A) #delete grammatical category
A <- gsub('\\s\\W','',A) #delete the big sapaces that appear before each word or combination of words
A <- strsplit(A,",")[[1]]
regex_pol <- paste(A,collapse = "|")
regex_pol <- tolower(regex_pol)
regex_pol <- gsub(' ','?',regex_pol)  #regex method allows for a better recognition than the inner_join method


#i also save the document as a dataframe
oxf_pol <- data.frame(word = A)

write.csv(oxf_pol,'oxf_pol.csv',row.names = F)

```

Another problem of this wordlist is that it doesn't include political figures' names or political organization names. Thus, we perform two name entity recognition of tweets from @nytimespolitics, @usatodayDC and @foxnewpolitics to find most popular and talked about political figures and organizations 

TO JUSTIFY NEWSPAPERS SELECTIONS: file:///C:/Users/user/Downloads/Political-Polarization-and-Media-Habits-FINAL-REPORT-7-27-15.pdf *(p.22)*

```{r}
#get tweets 
  newspapers <- get_timeline(c('nytpolitics','foxnewspolitics','usatodayDC'),1000)

#get names
politicians_or <- person_entity(newspapers$text)
organizations_or <- organization_entity(newspapers$text)

#get output of function into a usable format and selecting mos frequent
politicians <- data.frame(words = tolower((unlist(politicians_or))))
politicians <- politicians%>%
  count(words)%>%
  filter(n>3)

organizations <- data.frame(words = tolower((unlist(organizations_or))))
organizations <- organizations%>%
  count(words)%>%
  filter(n>3)

#some manual changes
  politicians <- politicians[-c(58,20,47,12,18,43,22,31),] #deleting some generic names (e.g. Jordan)
  politicians <- politicians%>%
    add_case(words = c('putin','trudeau','democr','republ'), n = rep(NA,4)) #adding some notable absences
  
  organizations <- organizations[-c(21,22,23,44,47),] #(e.g. us,hourse)

#creating the list with some useful properties
polits_list <- politicians$words

polits_list <- paste(polits_list,collapse = '|') #one single string that grep() will understand as any of this names
polits_list <- gsub(' ', '?',polits_list) #so even if spaces are omitted the name is identified

orgs_list <- organizations$words

orgs_list <- paste(orgs_list,collapse = '|') #one single string that grep() will understand as any of this names
orgs_list <- gsub(' ', '?',orgs_list) #so even if spaces are omitted the name is identified

entities_list <- paste(c(polits_list,orgs_list),collapse = '|')

```


Based on this political lexicon and names list, we asses how many of each user's last 100 tweets were political. This value is their *involvement score*. At some point the forloop is asking for too many tweets and it stops, it must then be done in batches


```{r}
IDs <- unique(active_users$user_id)

#matrix to store involvement  
pol_inv <- matrix(c(IDs,rep(0,2*length(IDs))),length(IDs),3)

#matrix to store a sample of categorized tweets to check the precision and recall of the method
samp <- matrix(c(IDs,rep(NA,2*length(IDs))),length(IDs),3)

#the loop itself

for(u in 860:length(IDs)){
  
  tl_try <- get_timeline(IDs[u])
  pol_tweets_n <- 0 #counter of political tweets for this particular user
  ind <- sample(1:length(tl_try$text),1) #to store a random tweet for evaluation
  figures <- 0 #a counter to see how relevant the figures and organization detection is
  
  if(length(tl_try$text)<1){#to ignore users that doesn't give access to their TL
    pol_inv[u,2] <- NA
    pol_inv[u,3] <- NA
  } else {
    
    for(i in 1:length(tl_try$text)){
      
      wrds <- grep(regex_pol, tolower(tl_try$text[i])) #see if theres any pol word in tweet
      if(length(wrds) > 0){
        pol_tweets_n <- pol_tweets_n + 1 #if POLITICAL WORDS > 0, add to counter
      } else {
        figs <- grep(entities_list,tolower(tl_try$text[i])) #see if political fig/orgs in tweets 
        if(length(figs)>0){
          pol_tweets_n <- pol_tweets_n + 1 #if POLITICAL FITURES found != 0, add to counter
          figures <- figures+1
        } 
      } 
      
      if(i == ind){   #store one random tweet & category per user for evaluation
        samp[u,2] <- tl_try$text[i]
        if (length(wrds) > 0|length(figs) > 0){
          samp[u,3] <- 'pol'
        } else {
          samp[u,3] <- 'not_pol'
        }
      }
    }
    
    pol_inv[u,2] <- pol_tweets_n #number of political tweets for this user
    pol_inv[u,3] <- length(tl_try$text) #keep track of how many total tweets we obtained from this user
    
  }
}


pol_inv_df <- data.frame(ID = pol_inv[,1],pol_tw =  as.numeric(pol_inv[,2]),pol_tot=as.numeric(pol_inv[,3])) #transformed into a dataframe
```

A graph showing distribution of *involvement* and another graph showing total number of tweets obtained. This last graph and the table are used to check to what extend we can use the absolute number of political tweets to compare individuals.

```{r}

ggplot(pol_inv_df, aes(pol_tw))+
  geom_histogram(bins = 40)

ggplot(pol_inv_df, aes(pol_tot))+
  geom_histogram(bins = 15)

table(pol_inv_df$pol_tot)
```


**4. Measure attitudes**

Using the *afinn* dictionary. 
```{r}

library(tidytext)

#Lexicon
sent_dic <- get_sentiments("afinn") 

#tokenize
X = 1:length(active_users$user_id)
active_users <- active_users%>%
  add_column(X)

bigrams <- active_users%>% #we need to group by X (i.e. post), otherwise considers all posts of user 1 same text
  group_by(X)

bigrams <- bigrams %>% 
  unnest_tokens(word, text, token = "ngrams", n = 2)%>%
  separate(word,c('word1','word2'), sep = " ")%>%
  inner_join(bigrams)

#negation words

neg = c('hardly','lack','neither','nor','never','no','nobody','none','nothing','nowhere','not','cannot','without')

bigrams <- bigrams%>%
  mutate(neg = ifelse(word1 %in% neg,-1,1))

#apply lexicon taking into account negation words
bigrams_sent <- bigrams %>%
  inner_join(sent_dic,by = c(word2 = 'word'))%>%
  mutate(value = value * neg)

#take into account sentiment words that are never in word2 (i.e. the first words in each tweet)
frst_wrd <- data.frame(screen_name = character(),word = character())

for(i in 1:length(active_users$text)){                      #we find the first word in each tweet
  words <- unnest_tokens(active_users[i,],word,text)
  frst_wrd <- frst_wrd%>%
    add_row(words[1,])
}

frst_wrd_sent <- frst_wrd%>%
  inner_join(sent_dic)%>%
  select(-word)

final_sent <- bigrams_sent%>%        #add first words with sentiment value to the data set
  group_by()%>%
  select(screen_name,value)%>%
  add_row(frst_wrd_sent)


#calculate sentiment per person
sentim <- final_sent %>% 
  mutate(screen_name = as.factor(screen_name)) %>% 
  group_by(screen_name) %>% 
  summarise(sent = mean(value)) 

hist(sentim$sent, breaks = 7)
sd(sentim$sent)/sqrt(length(sentim$sent))


```

**5. Relationship between **
Look for correlation between absolute attitudes and involvement and plot attitudes at four different levels of involvement. 
```{r}

last_tw <- sentim%>%
  inner_join(active_users)%>%
  select(ID = user_id,sent)%>%
  inner_join(pol_inv_df)%>%
  na.omit()%>%
  distinct()

library(forcats)

last_tw <- last_tw%>%
  mutate(quantilegroup = ntile(pol_tw, 4))%>%
  mutate(quantilegroup = factor(quantilegroup))

levels(last_tw$quantilegroup) <- c('Low','Mid-low','Mid-high','High')

last_tw %>% 
  mutate(quantilegroup = quantilegroup) %>% 
  ggplot(aes(x = sent, y = quantilegroup)) + 
  geom_density_ridges(fill = 'white',alpha = 0,lty = 1)+
  xlim(-5,5)+
  xlab('Sentiment')+
  ylab('Involvement')+
  theme_minimal()+
  theme(panel.grid.major.y = element_blank(),
        axis.ticks.x = element_line(color = 'grey95'),
        text = element_text(family = 'CMU Serif',size = 14))

fonttable()

last_tw %>%
  group_by(as.factor(quantilegroup))%>%
  summarise(mean(abs(sent)))


cor(abs(last_tw$sent),last_tw$pol_tw)

plot(last_tw$pol_tw,abs(last_tw$sent))

ggplot(last_tw,aes(pol_tw,abs(sent)))+
  geom_point(position = 'jitter')
```

**6. Fitting the cusp model**
```{r}
#create the data set to feed into the cusp function
data <- sentim%>%
  inner_join(tweets)%>%
  select(ID = user_id,sent)%>%
  unique()%>%
  inner_join(pol_inv_df)%>%
  select(-pol_tot,invol = pol_tw)%>%
  subset(!is.na(invol))


#fit the linear, restricted and unrestricted model 

library(cusp)

fit <- cusp(y ~ sent, alpha ~ 1, beta ~ invol, data) 

summary(fit)
summary(fit_logit)

#linear
linear <- lm(sent ~ invol,data)
summary(linear)

ggplot(data,aes(x = invol,y = sent))+
  geom_point(position = 'jitter', size = 0.5)+
  geom_smooth(method = 'lm',se = F,color = 'red',lwd = 0.7,lty = 1)+
  theme_bw()+
  xlab('Involvement')+
  ylab('Attitudes')
  scale_x_continuous(breaks = seq(0,100,10))+
  scale_y_continuous(breaks = seq(-5,5,1),limits = c(-5,5))+
  theme(panel.grid.minor = element_blank(),
        text = element_text(family = 'CMU Serif'))


#unrestricted 
summary(fit)


plot(fit)

fit2 <- cusp(y ~ sent, alpha ~ invol, beta ~ invol, data)  #unrestricted
summary(fit2)


cusp::plotCuspBifurcation(fit)

plotCuspBifurcation(fit)
```
**EXTRA: Checking the per post version of the political attitudes measurment**

```{r}
#did we average out extreme opinions?
sent <- get_sentiments('afinn')
n_tweets <- active_users%>%
  group_by(status_id)%>%
  unnest_tokens(word,text)%>%
  inner_join(sent)%>%
  summarise(sent = mean(value))%>%
  inner_join(active_users)%>%
  select(user_id,status_id,sent)%>%
  rename(ID = user_id)%>%
  inner_join(pol_inv_df)%>%
  subset(!is.na(pol_tw))%>%
  mutate(pol_tw_inv = 101 - pol_tw)


#Comparing the the two per_user and per_post design
#per tweet = 0
#per user = 1
lvn <- data.frame(sent = c(n_tweets$sent,data$sent),
           grp = c(rep(0,length(n_tweets$status_id)),rep(1,length(data$ID))))

leveneTest(lvn$sent,lvn$grp)

ggplot(lvn,aes(x = factor(grp),y = sent))+
  geom_boxplot()


###ggridges
n_tweets <- n_tweets%>%
  mutate(quantilegroup = ntile(pol_tw, 4))%>%
  mutate(quantilegroup = factor(quantilegroup))

levels(n_tweets$quantilegroup) <- c('Low','Mid-low','Mid-high','High')

combi1 <- n_tweets%>%
  select(sent,quantilegroup)%>%
  mutate(grp = 'Per Post')%>%
  mutate(grp = factor(grp))



  
combi2 <- last_tw%>%
  select(sent,quantilegroup)%>%
  mutate(grp = 'Per User')%>%
  mutate(grp = factor(grp),quantilegroup=factor(quantilegroup))%>%
  add_row(combi1)

levels(combi2$quantilegroup) <- c('Low','Mid-low','Mid-high','High')

  
head(combi1)
head(combi2)

combi2 %>% 
  ggplot(aes(x = sent, y = quantilegroup,fill = grp)) + 
  geom_density_ridges(alpha = 0.8,lty = 1)+
  xlim(-5,5)+
  xlab('Sentiment')+
  scale_fill_manual(values = c('Per post' = '#c6c6c6','Per user' = 'black'))+
  ylab('Involvement')+
  theme_bw()+
  theme(panel.grid.major.y = element_blank(),
        axis.ticks.x = element_line(color = 'grey95'),
        text = element_text(family = 'CMU Serif',size = 14))

```



